RNA-seq from 4 cell populations

### 2020-08-21 deconvolution/fans4/molec_profiling.Rmd
Initial commit

@@

geneInfo = df_featureCounts_gene[,1:6]
geneInfo$EnsId = gsub("^(.*)(\\.\\S+)$", "\\1", geneInfo$Geneid)

@@

# remove genes with duplicated EnsId
exclude = duplicated(geneInfo$EnsId)
geneInfo = geneInfo[!exclude,]
geneCounts = geneCounts[!exclude,]
rownames(geneCounts) = gsub("^(.*)(\\.\\S+)$", "\\1", rownames(geneCounts))

# convert to HUGO names
df_hugo = select(org.Hs.eg.db, geneInfo$EnsId, "SYMBOL", "ENSEMBL")
geneInfo = merge(geneInfo, df_hugo, by.x='EnsId', by.y="ENSEMBL")

>>>>

source("../../common_functions/common_functions.R")

@@

geneInfo = df_featureCounts_gene[,1:6]
geneInfo$EnsId = trim_ensembl_ids( geneInfo$Geneid )
geneInfo = geneInfo %>% getGeneSymbol( 'Geneid' )

@@

# remove genes with duplicated EnsId
exclude = duplicated(geneInfo$EnsId)
geneInfo = geneInfo[!exclude,]
geneCounts = geneCounts[!exclude,]
rownames(geneCounts) = trim_ensembl_ids( rownames(geneCounts) )

# convert to HUGO names
# df_hugo = select(org.Hs.eg.db, geneInfo$EnsId, "SYMBOL", "ENSEMBL")
# geneInfo = merge(geneInfo, df_hugo, by.x='EnsId', by.y="ENSEMBL")
